{ \sffamily \LARGE Electronic supplementary material}\\{\bf \sffamily \LARGE Evolution of reciprocity with limited payoff memory

### 2024-03-18 paper/si.tex
CH: Revising the SI

\noindent
This document provides further details on our methods and derivations, and it contains additional simulation results. 
Section~\ref{section:model} summarizes the model. 
In particular, we provide further details on our implementation of the evolutionary dynamics, and our use of the rare-mutation limit. 
In Section~\ref{section:analyticalresults}, we derive analytical results for the various settings we consider.
These settings differ in what kind of payoff information individuals take into account when updating their strategies. 
In the perfect-memory setting, individuals take into account all their interactions against all co-players.
In the limited-memory setting, they only consider the very last round of their very last interaction.  
In addition, we describe several model extensions in which the amount of information taken into account is in between these two extremes. 
Finally, Section~\ref{section:furthersimulations} presents further simulation results. 
In particular, we confirm that our main results continue to hold ({\it i}) when mutations are no longer rare, and  ({\it ii}) when players use memory-1 strategies instead of reactive strategies.

@@

\noindent
{\bf Summary of the model.} As described in the main text, we study cooperative behavior in a population of size $N$, with $N$ being even.
The dynamics unfold on two time scales. 
The short time scale describes the game dynamics. 
Here the $N$ individuals are randomly matched to form $N/2$ pairs to interact in a repeated prisoner's dilemma.  
Each round, individuals can choose whether to cooperate ($C$) or defect ($D$). 
In the most general setting, the resulting one-shot payoffs can be summarized by the payoff matrix 
\begin{align}
	\bordermatrix{%
		& C & D \cr
		C &\ R &\ S\  \cr
		D &\ T &\ P\ \cr
	} . \label{eq:prisoner}
\end{align}
Here, $R$ is interpreted as the reward for mutual cooperation, $S$ is the sucker's payoff, $T$ is the temptation, and $P$ is the punishment payoff~\citep{axelrod1981evolution}. 
Throughout this work, we parametrize these payoffs as $R\!=\!b\!-\!c$, $S\!=\!-c$, $T\!=\!b$, and $P\!=\!0$, where $b$ and $c$ are the benefit and cost of cooperation, respectively, with $b\!>\!c\!>0$. 
After each round, players learn their co-player's previous action. 
Then the game continues for another round with probability~$\delta$.
Players make their decisions whether to cooperate in any given round based on their reactive strategies $\strategy\!=\!(y,p,q)$. 
The entry $y$ determines a player's first-round cooperation probability. 
The other entries $p$ and $q$ determine the player's cooperation probability in all subsequent rounds. 
The probability is $p$ if the co-player cooperated in the previous round, and it is $q$ if the co-player defected. 
On this short time scale, the players' strategies are fixed, and players are consecutively matched to play repeated games with all other population members.

@@

\noindent
{\bf Evolutionary simulations for the rare-mutation limit.} 
To simulate the evolutionary dynamics of the pairwise comparison process, it is sometimes useful to assume that mutations are rare, $\mu\!\rightarrow\!0$. 
In that case, whenever a mutant strategy appears, it either fixes in the population or goes extinct before the next mutant appears. 
As a result, at any given time there are at most two different strategies present in the population~\citep{fudenberg:JET:2006,wu:JMB:2012,mcavoy:jet:2015}. 
This assumptions makes computations more efficient, and it makes some of the results easier to interpret.
In the following, we describe our implementation of the process in the rare-mutation limit in more detail.

@@

In the following, we discuss our different memory settings in more detail. 
We discuss six cases explicitly. In these cases, updating occurs
({\it i})~based on average payoffs based on all interactions (perfect memory), 
({\it ii})~based on the last round of one interaction (limited memory), 
({\it iii})~based on the last round of two interactions,
({\it iv})~based on the last two rounds of one interaction,
({\it v})~based on the last two rounds of two interactions, and
({\it v})~based on the average payoff of one interaction.
In each case, we assume there are only two strategies present in the population (a resident and a mutant strategy). 
We first derive how likely it is that a learner (of any type) assigns a given payoff $\pi_\learner$ to itself, and a payoff of $\pi_\rolemodel$ to the role model. 
This allows us to derive explicit expressions for $\lambda^-_k/\lambda^+_k$, and hence for the mutant's fixation probability according to Eq.~\eqref{eq:fixation_probability}.
Based on these expressions we can characterize under which conditions cooperation is stochastically stable.

@@

\begin{equation}
  \frac{\lambda^{-}_1}{\lambda^{+}_1} =
  \frac{1 + e^{- \beta \left(b \left(\delta q - \delta\right) + c\right)}}{1 + e^{\beta \left(b \left(\delta q - \delta\right) + c\right)}}.
\end{equation}
For stochastic stability of cooperation we require this ratio to be larger than one, which is equivalent to
\begin{equation} \label{Eq:Condition_OneInteractionExpectedPayoff}
  q<1 - \frac{c}{\delta b}
\end{equation}
Interestingly, this condition is the same as condition~\eqref{Eq:Condition_PerfectMemory} for the case of perfect memory when $N\! \rightarrow\! \infty$.

@@

\section{Further simulation results}
\label{section:furthersimulations}

@@

\section{Further repeated games; Snowdrift game}
\label{section:furtherrepeatedgames}

So far, we have discussed the repeated donation game, which is only one example
of social dilemmas. In the following section, we explore how our methodology can
be applied to other games, with a focus on the snowdrift game.

Similar to the donation game, the snowdrift game is a two-player game where
individuals choose to cooperate (\(C\)) or defect (\(D\)) each round.
Cooperation yields a benefit \(b\) to both players, incurring a cost \(c\) if
the opponent defects, but only \(c/2\) if the opponent cooperates. This results
in the following payoff matrix

\begin{align}
	\bordermatrix{%
		& C & D \cr
		C & b - \frac{c}{2} & b - c  \cr
		D & b & 0 \cr
	} . 
\end{align}\label{eq:snowdrift_payoff}

In the following subsections, we discuss how our results extend to the snowdrift
game. In Section~\ref{section:stochastic_stability_snowdrift}, we investigate
under which conditions cooperation is stochastically stable for both perfect and
limited memory scenarios. In Section~\ref{section:simulation_results_snowdrift},
we present simulation results for all six cases considered in this study.

\subsection{Stochastic stability of cooperation.}\label{section:stochastic_stability_snowdrift}

{\bf Perfect payoff memory.} We have already discussed the general setup for the
case of perfect memory in Section~\ref{section:perfect_memory}. Here, we derive
the conditions under which cooperation is stochastically stable for the
snowdrift game. As a reminder, we suppose that there is a single mutant,
\(k\!=\!1\) that adopts the strategy $\alld$, while the residents adopt the
strategy \(\gtft\). The resulting average distributions between the residents
and the mutants remain the same as in Section\ref{section:perfect_memory}.
However, the expected payoffs of the strategies now differ, as we are now
considering the snowdrift payoff matrix~\eqref{eq:snowdrift_payoff}. \\

\noindent
Specifically, the expected payoffs are computed as,

\begin{align*}
  \pi_\gtft =  \frac{N\!-\!2}{N-1} (b - c/2)  \!+\! \frac{1}{N-1}\big(1\!-\!\delta\!+\!\delta q\big)(b - c)
  \quad \text{and} \quad
  \pi_\alld  = \big(1\!-\!\delta\!+\!\delta q\big)b.
\end{align*}

As a consequence, the corresponding ratio of transition probabilities according
to Eq.~\eqref{eq:LambdaRatio} is now given by,

\begin{align*}
\frac{\lambda_1^{-}}{\lambda_1^{+}} = e^{-\beta \left( (1-\delta+\delta q)(b - \frac{b-c}{N-1})- \frac{N-2}{N-1}(b-c/2) \right)}
\end{align*}
By definition, cooperation is stochastically stable if this ratio exceeds one, which is equivalent to
\begin{equation}\label{Eq:Condition_PerfectMemory_Snowdrift}
q<1-\frac{1}{\delta}\cdot \frac{N(c/2)}{(N\!-\!2)b+c}.
\end{equation}
For such a strategy to be feasible we require $q\!>\!0$, which implies $\delta
\!>\! \big((N\!-\!2)b+c\big)/\big(N(c/2)\big)$. In particular, in the limit of
large populations \(N \!\rightarrow\! \infty\), we obtain that cooperation is
stochastically stable if  \(q \!<\! 1\! -\! c/(2\delta b)\). \\

\noindent
{\bf Limited payoff memory.} Once again, we examine
the scenario where a single \alld{} mutant can potentially invade a resident
population of \gtft{} players. However, this time, we consider that individuals
only take into account the last round of their last interaction.
Based on the probabilities \(x(u_\resident,u_\mutant)\), where \(u_\resident\)
represents the payoff of a randomly chosen \gtft{} player and \(u_\mutant\)
represents the payoff of the \alld{} player, with both \(u_\resident\) and
\(u_\mutant\) being elements of \(\mathcal{U}\) (see
Section~\ref{section:limited_memory}), we calculate the ratio of transition
probabilities as:

\begin{equation*}
\frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{ \frac{N - 2}{N - 1}  
\left(\frac{ 1 - \delta + \delta q}{1+e^{ \beta (c/2)} } 
  + \frac{ \delta  \left(1 - q \right)}{1+ e^{-  \beta  \left(b - c/2 \right)}} \right)  
  +  \frac{1}{N-1}  \left(\frac{1 - \delta + \delta q}{1 + e^{\beta c}}
  + \frac{ \delta  \left(1 - q \right)}{2} \right)}
  { \frac{N - 2}{N - 1}  
\left( \frac{ 1 - \delta + \delta q}{1 + e^{-\beta (c/2)}}
+  \frac{ \delta  (1 - q)}{1 +e^{  \beta (b - c/2)}} \right) 
+  \frac{1}{N -1} \left(\frac{ 1 - \delta + \delta q}{1 + e^{-  \beta c}}
+  \frac{ \delta  \left(1 - q \right)}{2} \right)} .
\end{equation*}
Cooperation is stochastically stable if $\lambda^-_1/\lambda^+_1\!>\!1$. 
We consider the limit of strong selection \(\beta\! \rightarrow\! \infty\) and
large populations \(N \!\rightarrow \!\infty \). In that case, because $b\!>\!c\!>\!0$, the above ratio simplifies to
\begin{equation}\label{Eq:Condition_LimitedMemory_Snowdrift}
    \frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{\delta(1 - q)}{1 - \delta + \delta q}.
\end{equation}

Interestingly, this condition is identical to
condition~\eqref{Eq:TransitionRatioSimple} for the donation game. To understand
this result, we first need to discuss the difference between the two games. The
difference between the two games lies in the relationship between the possible
payoffs. More specifically, in the donation game, the payoffs satisfy the
relationship \(T > R > P > S\), whereas in the snowdrift game, it's \(T > R > S
> P\).
Now, note that for the above condition, the relationship between all the
possible payoffs is not important; what is important is the relationship between
all the feasible pairs of payoffs. In a population of \gtft{} strategies with a
single mutant of \alld{}, the feasible pairs of payoffs are \((R, T)\), \((R,
P)\), \((S, T)\), and \((P, P)\). In both games, the payoff \(T\) is higher than
\(S\) and \(R\), and \(R\) is higher than the punishment payoff, thus the
condition remains unchanged.

\subsection{Simulation results for reactive strategies}\label{section:simulation_results_snowdrift}

To investigate whether the previous static observations accurately depict the
dynamics of evolving populations, we once again rely on simulations. Firstly, we
conducted separate simulations for perfect and limited payoff memory. In each
scenario, we examined both low and high benefits of cooperation (\(b/c=2\) and
\(b/c=10\), respectively). Supplementary Fig.
\ref{fig:expected_and_stochastic_for_snowdrift} illustrates the conditional
cooperation probabilities \(p\) and \(q\) of the evolving populations. Overall,
we find that the evolving populations are more cooperative compared to those of
the donation game. There is no cluster around the neighborhood of \alld{} as
they are easily outperformed by more cooperative strategies. Moreover, the
evolving cooperation rates are high for all the cases. Even in the limited
payoff memory for low benefit, the evolving cooperation is at 71\%. Thus, the
in the snowdrift game, the memory requirement for cooperation is
even more modest compared to the donation game.

\begin{figure}[t]
  \centering
  \includegraphics[width=.75\textwidth]{static/snowdrift_game_results.pdf}
  \caption{{\bf Evolutionary dynamics under perfect and limited payoff memory.}
The four panels depict the outcome of evolutionary simulations for the repeated
snowdrift game with either a low or high benefit of cooperation. In the top
panels, individuals have perfect payoff memory, meaning they consider all their
past interactions against all population members, taking every turn of each
repeated game into account. In the bottom panels, individuals have limited
payoff memory, considering only their very last interaction against one specific
population member, and taking into account only one round of the repeated game.
Colors represent how often the respective region of the strategy space is
visited over time.
In all cases, there is one dominant cluster, and that is the cluster of
conditionally cooperative strategies with \(p \approx 1\), where \(q\) satisfies
the constraints \eqref{Eq:Condition_PerfectMemory_Snowdrift} and
\eqref{Eq:Condition_LimitedMemory_Snowdrift}, respectively.
Simulations are run for \(T = 10^7\) time steps, using a cost \(c = 1\), a
continuation probability of \(\delta = 0.999\), and a selection strength of
\(\beta = 1\), in a population of size \(N = 100\).}
\label{fig:expected_and_stochastic_for_snowdrift}
\end{figure}

Furthermore, to understand the impact of payoff memory on the snowdrift game
even more, we performed simulations for the four additional scenarios considered
in this work. As a reminder, in the first scenario, players recall the payoffs
they obtained in the last two rounds against a single co-player. In the second
scenario, players recall their last-round payoffs against two co-players. In the
third scenario, they recall the last two rounds against two co-players. Finally,
in the last scenario, players update based on the average payoff they receive
over all rounds with a single co-player (further extensions are possible, but we
do not explore them here). In Supplementary
Fig.~\ref{fig:cooperation_rate_all_updating_payoffs_snowdrift}, we show the
evolving cooperation rates for all these scenarios, as well as for the limited
and perfect memory cases.

We observe that main pattern of our results remains unchanged: the perfect
memory case always overestimates the cooperation rate. Compared to the baseline
case with a single round recalled, even a minimal increase in the players'
payoff memory further increases the cooperation rate. In all four scenarios with
extended memory, we observe similar cooperation rates, and they quickly approach
the rates observed under perfect memory. This happens at a faster rate compared
to the donation game.

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{static/snowdrift_game_more_memory.pdf}
  \caption{{\bf Average cooperation rates in the snowdrift game for different payoff memories.}
  We vary how much information individuals take into account when updating their strategies.
  From left to right, we consider the following cases:
  ({\it i}) Updating occurs based on expected payoffs (perfect memory).
  ({\it ii}) It occurs based on the last round of one interaction (limited memory).
  ({\it iii}) Based on the last round of two interactions.
  ({\it iv}) Based on the last two rounds of one interaction.
  ({\it v}) Based on the last two rounds of two interactions.
  ({\it vi}) Based on the average payoff of one interaction.
  Simulations are run either for a comparably low benefit of cooperation~($b/c\!=\!2$), or for a high benefit~($b/c\!=\!10$). 
  We observe that perfect memory always yields the highest cooperation rate, and limited memory yields the lowest.
  However, in the snowdrift game, the difference between the two extreme scenarios is not large, as we have already discussed.
  When individuals take into account a bit more information—cases (iii) to (vi)—evolving
  cooperation rates quickly approach the optimum of perfect memory. This increase happens faster compared to the donation game.
  Simulations are run for $T\!=\!10^7$ time steps, using a cost $c\!=\!1$, a continuation probability of $\delta\!=\!0.999$ and a selection strength of $\beta\!=\!1$, in a population of size $N\!=\!100$.}
\label{fig:cooperation_rate_all_updating_payoffs_snowdrift}
\end{figure}

>>>>

\noindent
This document provides further details on our methods and derivations, and it contains additional simulation results. 
Section~\ref{section:model} summarizes the model. 
In particular, we provide further details on our implementation of the evolutionary dynamics, and our use of the rare-mutation limit. 
In Section~\ref{section:analyticalresults}, we derive analytical results for the various settings we consider.
These settings differ in what kind of payoff information individuals take into account when updating their strategies. 
In the perfect-memory setting, individuals take into account all their interactions against all co-players.
In the limited-memory setting, they only consider the very last round of their very last interaction.  
In addition, we describe several model extensions in which the amount of information taken into account is in between these two extremes. 
Finally, Section~\ref{section:furthersimulations} presents further simulation results and model extensions. 
In particular, we confirm that our main results continue to hold ({\it i}) when mutations are no longer rare, ({\it ii}) when players use memory-1 strategies instead of reactive strategies, and ({\it iii}) when players interact in a snowdrift game.

@@

\noindent
{\bf Summary of the model.} As described in the main text, we study cooperative behavior in a population of size $N$, with $N$ being even.
The dynamics unfold on two time scales. 
The short time scale describes the game dynamics. 
Here the $N$ individuals are randomly matched to form $N/2$ pairs to interact in a repeated prisoner's dilemma.  
Each round, individuals can choose whether to cooperate ($C$) or defect ($D$). 
In the most general setting, the resulting one-shot payoffs can be summarized by the payoff matrix 
\begin{align}
	\bordermatrix{%
		& C & D \cr
		C &\ R &\ S\  \cr
		D &\ T &\ P\ \cr
	} . \label{eq:prisoner}
\end{align}
Here, $R$ is interpreted as the reward for mutual cooperation, $S$ is the sucker's payoff, $T$ is the temptation, and $P$ is the punishment payoff~\citep{axelrod1981evolution}. 
For most of this work, we parametrize these payoffs as $R\!=\!b\!-\!c$, $S\!=\!-c$, $T\!=\!b$, and $P\!=\!0$, where $b$ and $c$ are the benefit and cost of cooperation, respectively, with $b\!>\!c\!>0$. 
After each round, players learn their co-player's previous action. 
Then the game continues for another round with probability~$\delta$.
Players make their decisions whether to cooperate in any given round based on their reactive strategies $\strategy\!=\!(y,p,q)$. 
The entry $y$ determines a player's first-round cooperation probability. 
The other entries $p$ and $q$ determine the player's cooperation probability in all subsequent rounds. 
The probability is $p$ if the co-player cooperated in the previous round, and it is $q$ if the co-player defected. 
On this short time scale, the players' strategies are fixed, and players are consecutively matched to play repeated games with all other population members.

@@

\noindent
{\bf Evolutionary simulations for the rare-mutation limit.} 
To simulate the evolutionary dynamics of the pairwise comparison process, it is sometimes useful to assume that mutations are rare, $\mu\!\rightarrow\!0$. 
In that case, whenever a mutant strategy appears, it either fixes in the population or goes extinct before the next mutant appears. 
As a result, at any given time there are at most two different strategies present in the population~\citep{fudenberg:JET:2006,wu:JMB:2012,mcavoy:jet:2015}. 
This assumption makes computations more efficient, and it makes some of the results easier to interpret.
In the following, we describe our implementation of the process in the rare-mutation limit in more detail.

@@

In the following, we discuss our different memory settings in more detail. 
We discuss six cases explicitly. In these cases, updating occurs
({\it i})~based on average payoffs based on all interactions (perfect memory), 
({\it ii})~based on the last round of one interaction (limited memory), 
({\it iii})~based on the last round of two interactions,
({\it iv})~based on the last two rounds of one interaction,
({\it v})~based on the last two rounds of two interactions, and
({\it vi})~based on the average payoff of one interaction.
In each case, we assume there are only two strategies present in the population (a resident and a mutant strategy). 
We first derive how likely it is that a learner (of any type) assigns a given payoff $\pi_\learner$ to itself, and a payoff of $\pi_\rolemodel$ to the role model. 
This allows us to derive explicit expressions for $\lambda^-_k/\lambda^+_k$, and hence for the mutant's fixation probability according to Eq.~\eqref{eq:fixation_probability}.
Based on these expressions we can characterize under which conditions cooperation is stochastically stable.

@@

\begin{equation}
  \frac{\lambda^{-}_1}{\lambda^{+}_1} =
  \frac{1 + e^{- \beta \left(b \left(\delta q - \delta\right) + c\right)}}{1 + e^{\beta \left(b \left(\delta q - \delta\right) + c\right)}}.
\end{equation}
For stochastic stability of cooperation we require this ratio to be larger than one, which is equivalent to
\begin{equation} \label{Eq:Condition_OneInteractionExpectedPayoff}
  q<1 - \frac{c}{\delta b}
\end{equation}
This condition is the same as condition~\eqref{Eq:Condition_PerfectMemory} for the case of perfect memory when $N\! \rightarrow\! \infty$. This result is intuitive: in infinitely large populations, we can ignore the possibility that the learner and the role model interacted directly immediately prior to the updating stage. Given that, their expected payoff in a single repeated game with their last interaction partner is identical to their expected payoff across all repeated games, with all possible interaction partners. 
\clearpage

@@

\section{Further simulation results and model extensions}
\label{section:furthersimulations}

@@

\subsection{An analysis of the snowdrift game}
\label{section:furtherrepeatedgames}

So far, we have discussed the repeated donation game, which is only one example
of a social dilemma. In the following section, we apply our methodology to a different dilemma, the snowdrift game.
Similar to the donation game, the snowdrift game is a two-player game where each round, 
individuals can choose to cooperate~(\(C\)) or to defect~(\(D\)).
If at least one player cooperates, both players get a benefit \(b\). 
A cooperator pays a cost of \(c\) if the opponent defects, and of \(c/2\) if the opponent cooperates. This results
in the following payoff matrix
\begin{equation} \label{eq:snowdrift_payoff}
	\bordermatrix{%
		& C & D \cr
		C & b - \frac{c}{2} & b - c  \cr
		D & b & 0 \cr
	} . 
\end{equation}
In the following subsections, we discuss how our results extend to the snowdrift
game. In Section~\ref{section:stochastic_stability_snowdrift}, we investigate
under which conditions cooperation is stochastically stable for both perfect and
limited memory. In Section~\ref{section:simulation_results_snowdrift},
we present simulation results.

\subsubsection{Stochastic stability of cooperation.}\label{section:stochastic_stability_snowdrift}

{\bf Perfect payoff memory.} As before, we suppose that there is a single mutant,
\(k\!=\!1\) that adopts the strategy $\alld$, while the residents adopt the
strategy \(\gtft\). The resulting average distributions between the residents
and the mutants remain the same as in Section~\ref{section:perfect_memory}.
However, the expected payoffs of the strategies now differ, as we are now
considering the snowdrift payoff matrix~\eqref{eq:snowdrift_payoff}. \\

\noindent
Specifically, the expected payoffs are computed as,
\begin{equation*}
  \pi_\gtft =  \frac{N\!-\!2}{N-1} (b - c/2)  \!+\! \frac{1}{N-1}\big(1\!-\!\delta\!+\!\delta q\big)(b - c)
  \quad \text{and} \quad
  \pi_\alld  = \big(1\!-\!\delta\!+\!\delta q\big)b.
\end{equation*}
As a consequence, the corresponding ratio of transition probabilities according
to Eq.~\eqref{eq:LambdaRatio} is now given by
\begin{align*}
\frac{\lambda_1^{-}}{\lambda_1^{+}} = e^{-\beta \left( (1-\delta+\delta q)(b - \frac{b-c}{N-1})- \frac{N-2}{N-1}(b-c/2) \right)}
\end{align*}
By definition, cooperation is stochastically stable if this ratio exceeds one, which is equivalent to
\begin{equation}\label{Eq:Condition_PerfectMemory_Snowdrift}
q<1-\frac{1}{\delta}\cdot \frac{N(c/2)}{(N\!-\!2)b+c}.
\end{equation}
For such a strategy to be feasible we require $q\!\ge\!0$, which implies $\delta
\!\ge\! \big((N\!-\!2)b+c\big)/\big(N(c/2)\big)$. In particular, in the limit of
large populations \(N \!\rightarrow\! \infty\), we obtain that cooperation is
stochastically stable if  \(q \!<\! 1\! -\! c/(2\delta b)\). \\

\noindent
{\bf Limited payoff memory.} Now we assume that individuals
only take into account the last round of their last interaction.
Based on the probabilities \(x(u_\resident,u_\mutant)\), where \(u_\resident\)
represents the payoff of a randomly chosen \gtft{} player and \(u_\mutant\)
represents the payoff of the \alld{} player, with both \(u_\resident\) and
\(u_\mutant\) being elements of \(\mathcal{U}\) (see
Section~\ref{section:limited_memory}), we calculate the ratio of transition
probabilities as:

\begin{equation*}
\frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{ \frac{N - 2}{N - 1}  
\left(\frac{ 1 - \delta + \delta q}{1+e^{ \beta (c/2)} } 
  + \frac{ \delta  \left(1 - q \right)}{1+ e^{-  \beta  \left(b - c/2 \right)}} \right)  
  +  \frac{1}{N-1}  \left(\frac{1 - \delta + \delta q}{1 + e^{\beta c}}
  + \frac{ \delta  \left(1 - q \right)}{2} \right)}
  { \frac{N - 2}{N - 1}  
\left( \frac{ 1 - \delta + \delta q}{1 + e^{-\beta (c/2)}}
+  \frac{ \delta  (1 - q)}{1 +e^{  \beta (b - c/2)}} \right) 
+  \frac{1}{N -1} \left(\frac{ 1 - \delta + \delta q}{1 + e^{-  \beta c}}
+  \frac{ \delta  \left(1 - q \right)}{2} \right)} .
\end{equation*}
Cooperation is stochastically stable if $\lambda^-_1/\lambda^+_1\!>\!1$. 
We consider the limit of strong selection \(\beta\! \rightarrow\! \infty\) and
large populations \(N \!\rightarrow \!\infty \). In that case, because $b\!>\!c\!>\!0$, the above ratio simplifies to
\begin{equation}\label{Eq:Condition_LimitedMemory_Snowdrift}
    \frac{\lambda^{-}_1}{\lambda^{+}_1} = \frac{\delta(1 - q)}{1 - \delta + \delta q}.
\end{equation}
Interestingly, this condition is identical to
condition~\eqref{Eq:TransitionRatioSimple} for the donation game. To understand
this result, we first need to discuss the difference between the two games. 
In the donation game, the payoffs satisfy the
relationship \(T \!>\! R \!>\! P \!>\! S\), whereas in the snowdrift game, the respective ordering is \(T \!>\! R \!>\! S
\!>\! P\).
Note that for the stochastic stability of \gtft, the relationship between all the
possible payoffs is not important; what is important is the relationship between
all the feasible pairs of payoffs. In a \gtft{} population  with a
single \alld{} mutant, the feasible payoff pairs are \((R, T)\), \((R,
P)\), \((S, T)\), \((P, P)\). In all these four cases, the relative ranking of the two payoffs remains unchanged.

\subsubsection{Simulation results for reactive strategies}\label{section:simulation_results_snowdrift}

In addition to these static observations, we again explore the evolutionary dynamics with simulations. 
Firstly, we conducted separate simulations for perfect and limited payoff memory. In each
scenario, we examined both low and high benefits of cooperation (\(b/c=2\) and
\(b/c=10\), respectively). Supplementary Fig.
\ref{fig:expected_and_stochastic_for_snowdrift} illustrates the conditional
cooperation probabilities \(p\) and \(q\) of the evolving populations. Overall,
we find that the evolving populations are more cooperative compared to those of
the donation game. There is no cluster around the neighborhood of \alld{} as
they are easily outperformed by more cooperative strategies. Moreover, the
evolving cooperation rates are high for all the cases. Even for limited
payoff memory and a low benefit, the evolving cooperation is at 71\%. Thus, 
in the snowdrift game, the memory requirement for cooperation is
even more modest compared to the donation game.

\begin{figure}[t]
  \centering
  \includegraphics[width=.75\textwidth]{static/snowdrift_game_results.pdf}
  \caption{{\bf Evolutionary dynamics for the snowdrift game under perfect and limited payoff memory.}
The four panels depict the outcome of evolutionary simulations for the repeated
snowdrift game with either a low or high benefit of cooperation. 
Colors represent how often the respective region of the strategy space is
visited over time.
In all cases, there is one dominant cluster, and that is the cluster of
conditionally cooperative strategies with \(p \approx 1\), where \(q\) satisfies
the constraints \eqref{Eq:Condition_PerfectMemory_Snowdrift} and
\eqref{Eq:Condition_LimitedMemory_Snowdrift}, respectively.
Simulations are run for \(T = 10^7\) time steps, using a cost \(c = 1\), a
continuation probability of \(\delta = 0.999\), and a selection strength of
\(\beta = 1\), in a population of size \(N = 100\).}
\label{fig:expected_and_stochastic_for_snowdrift}
\end{figure}

Again, we performed similar simulations when the players' payoff memory is 
in between the two extremes of perfect and limited memory (Supplementary
Fig.~\ref{fig:cooperation_rate_all_updating_payoffs_snowdrift}).
The main patterns of our previous results remain unchanged: ({\it i})~Perfect
memory always yields the highest cooperation rate; ({\it ii})~Compared to the 
case with a single round recalled, even a minimal increase in the players'
memory further increases cooperation; ({\it iii})~In all scenarios with
intermediate memory, we observe similar cooperation rates, and they quickly approach
the rates observed under perfect memory.

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{static/snowdrift_game_more_memory.pdf}
  \caption{{\bf Average cooperation rates in the snowdrift game for different payoff memories.}
  Again, we vary how much information individuals take into account when updating their strategies.
  Simulations are run either for a low benefit of cooperation~($b/c\!=\!2$), or for a high benefit~($b/c\!=\!10$). 
  We observe that perfect memory always yields the highest cooperation rate, and limited memory yields the lowest.
  However, in the snowdrift game, the difference between the two extreme scenarios is smaller than in the donation game. 
  When individuals take into account a bit more information, evolving cooperation rates quickly approach the optimum of perfect memory. 
  Simulations are run for $T\!=\!10^7$ time steps, using a cost $c\!=\!1$, a continuation probability of $\delta\!=\!0.999$ and a selection strength of $\beta\!=\!1$, in a population of size $N\!=\!100$.}
\label{fig:cooperation_rate_all_updating_payoffs_snowdrift}
\end{figure}
